Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-02-22 summary_minh_edited.tex
minor adjustments for submission

\item[Code:] The code is not uploaded here but can be found online at \\
\url{https://github.com/johneverettkoo/pabm-grdpg}.

>>>>

\item[Code:] The code for simulations and data anlyses can be found in code-and-results.zip. 
This file also includes the simulation results in csv format (please note that the simulations can take a long time to complete). 
The code for data analyses requires the files found in data.zip. 
All of these files can also be found at\\
\url{https://github.com/johneverettkoo/pabm-grdpg}.

\item[Sparsity:] Additional supplemental materials regarding simulations for the effect of the sparsity parameter can be found in sparsity-sim.zip.
